H1 Supplement

### 2023-02-10 H1.Rmd
heat maps and flag plots added

@@

g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.001, color="lightgrey")+
  geom_violin(fill = NA) +
  #ggforce::geom_sina(size=.01)+
  # geom_sina(shape=16
  #           , position=position_jitter(height=.25,width=0)
  #           , size=.000001
  #           , color="dark grey"
  #           ,jitter_y=F
  # )+
  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
               position=position_dodge(0.05), color="#5a5a5a")+
  stat_summary(fun=mean, geom="point", shape=16, size=2)+
  # stat_summary(geom = "linerange",
  #   fun.data = mean_sdl, 
  #   fun.args = list(mult = 1),
  #   colour = "black"
  # )+
  xlab("Gender")+
  ylab("Internalization")+  
  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

@@

# df1 <- df
g2 <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.001, color="lightgrey")+
  geom_violin(fill = NA) +
  #ggforce::geom_sina(size=.01)+
  # geom_sina(shape=16
  #           , position=position_jitter(height=.25,width=0)
  #           , size=.000001
  #           , color="dark grey"
  #           ,jitter_y=F
  # )+
  #geom_quasirandom(size=.1)+
  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
               position=position_dodge(0.05), color="#5a5a5a")+
  stat_summary(fun=mean, geom="point", shape=16, size=2)+
  # stat_summary(geom = "linerange",
  #   fun.data = mean_sdl, 
  #   fun.args = list(mult = 1),
  #   colour = "black"
  # )+
  xlab("Gender")+
  ylab("Symbolization")+  
  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

>>>>

## Internalization

alpha_generic <- function(x){
  df <- x

  df$moralid4R <- reverse.code(c(-1), df$moralid4)
  df$moralid7R <- reverse.code(-1, df$moralid7)

  y <- subset(df,select=c(
    moralid1
    , moralid2
    , moralid4R
    , moralid7R
    , moralid10
  ))
  cronbach.alpha(y[complete.cases(y),])
}

alpha_generic(df)

## Symbolization

alpha_generic <- function(x){
  df <- x
  y <- subset(df,select=c(
    moralid3
  , moralid5
  , moralid6
  , moralid8
  , moralid9
))
  cronbach.alpha(y[complete.cases(y),])
}

alpha_generic(df)

@@

g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.001, color="lightgrey")+
  geom_violin(fill = NA) +
  #ggforce::geom_sina(size=.01)+
  # geom_sina(shape=16
  #           , position=position_jitter(height=.25,width=0)
  #           , size=.000001
  #           , color="dark grey"
  #           ,jitter_y=F
  # )+
  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
               position=position_dodge(0.05), color="#5a5a5a")+
  stat_summary(fun=mean, geom="point", shape=16, size=2)+
  # stat_summary(geom = "linerange",
  #   fun.data = mean_sdl, 
  #   fun.args = list(mult = 1),
  #   colour = "black"
  # )+
  xlab("Gender")+
  ylab("Internalization")+  
  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
       # panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

@@

# df1 <- df
g2 <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.001, color="lightgrey")+
  geom_violin(fill = NA) +
  #ggforce::geom_sina(size=.01)+
  # geom_sina(shape=16
  #           , position=position_jitter(height=.25,width=0)
  #           , size=.000001
  #           , color="dark grey"
  #           ,jitter_y=F
  # )+
  #geom_quasirandom(size=.1)+
  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
               position=position_dodge(0.05), color="#5a5a5a")+
  stat_summary(fun=mean, geom="point", shape=16, size=2)+
  # stat_summary(geom = "linerange",
  #   fun.data = mean_sdl, 
  #   fun.args = list(mult = 1),
  #   colour = "black"
  # )+
  xlab("Gender")+
  ylab("Symbolization")+  
  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
     #   panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

### 2023-02-10 H2.Rmd
heat maps and flag plots added

We conducted a linear-mixed-effects model to test if this relationship between age and internalization holds when participants are nested within country. Our outcome measure was internalization and our predictor variable was age; we allowed intercepts to vary by country.
Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for age,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
We conducted a series of correlations test if age was related to internalization across all countries.  There was a significant correlation between age and internalization in `r total_sig` countries. Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Internalization)).

@@

Similarly, for symbolization, we conducted a linear-mixed-effects model to test if the relationship between age and symbolization holds when participants are nested within country. Our outcome measure was symbolization and our predictor variable was age; we allowed intercepts to vary by country.
Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for age,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
We conducted a series of correlations test if age was related to internalization across all countries.  There was a significant correlation between age and internalization in `r total_sig` countries. Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Symbolization)).

>>>>

We conducted a linear-mixed-effects model to test if this relationship between age and internalization holds when participants are nested within country. Our outcome measure was internalization and our predictor variable was age; we allowed intercepts to vary by country.
Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for age,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
To interpret this we conducted a series of bivariate correlations to test if age was related to internalization across all countries.  There was a significant correlation between age and internalization in `r total_sig` countries. Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Internalization)).

@@

Similarly, for symbolization, we conducted a linear-mixed-effects model to test if the relationship between age and symbolization holds when participants are nested within country. Our outcome measure was symbolization and our predictor variable was age; we allowed intercepts to vary by country.
Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for age,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
Again, to interpret this, we conducted a series of correlations to test if age was related to internalization across all countries.  There was a significant correlation between age and internalization in `r total_sig` countries. Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Symbolization)).

### 2023-02-10 H3.Rmd
heat maps and flag plots added

```{r}
rm(list = ls())
library(tidyverse)
library(plyr)
library(psych)
library(skimr)
library(corrplot)
library(Hmisc)
#library(psy)
library(afex)
#devtools::install_github("cillianmiltown/R_desnum")
library(desnum)
library(papaja)
library(purrr)
#install.packages("interactions")
library(interactions)
library(kableExtra)
#devtools::install_github("crsh/papaja")
library("papaja")
library(lme4)
library(car)
library(ggplot2)
library(nlme)
#install.packages("reshape")
library(reshape)
library(corx)
library(lsr)
#install.packages("Cairo")
#library(Cairo)
library(foreign)
library(ltm)
library("ggpubr")
#install.packages("rworldmap")
library(rworldmap)
#devtools::install_github("rensa/ggflags")
library(ggflags)
#devtools::install_github("schliebs/ggoxford")
library(ggoxford)
library(ggforce)
library(ggbeeswarm)
library(countrycode)
```

@@

fit0 <- lm(moral_identity_symbolic ~ 
             mean(x$moral_identity_symbolic)
                    # sex3
                    # + age
                    #  Power.Distance
                    # + Individualism
                    # + Masculinity
                    # + Uncertainty.Avoidance
                    # + Long.Term.Orientation
                    # + Indulgence
                    # + CTL_C
                    # + CTL_DS
                    # + CTL_DG
                 , data = x
            )

summary(fit0)

fit <- lm(moral_identity_symbolic ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)
anova(fit)
fit_results <- apa_print(fit)

@@

fit_results$full_result

@@

>>>>

```{r}
rm(list = ls())
library(tidyverse)
library(plyr)
library(psych)
library(skimr)
library(corrplot)
library(Hmisc)
#library(psy)
library(afex)
#devtools::install_github("cillianmiltown/R_desnum")
library(desnum)
library(papaja)
library(purrr)
#install.packages("interactions")
library(interactions)
library(kableExtra)
#devtools::install_github("crsh/papaja")
library("papaja")
library(lme4)
library(car)
library(ggplot2)
library(nlme)
#install.packages("reshape")
library(reshape)
library(corx)
library(lsr)
#install.packages("Cairo")
#library(Cairo)
library(foreign)
library(ltm)
library("ggpubr")
#install.packages("rworldmap")
library(rworldmap)
#devtools::install_github("rensa/ggflags")
library(ggflags)
#devtools::install_github("schliebs/ggoxford")
library(ggoxford)
library(ggforce)
library(ggbeeswarm)
library(countrycode)

@@

fit <- lm(moral_identity_symbolic ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    # + Long.Term.Orientation
                    # + Indulgence
                    # + CTL_DG
                    # + CTL_DS
                    # + CTL_C
                , data = x
            )
fit
fit_results <- summary(fit)
fit_results

fit_results$adj.r.squared
anova(fit)
apa_fit_results <- apa_print(fit)

@@

apa_fit_results$full_result$modelfit$r2
fit$qr
apa_fit_results$table
results_for_table <- apa_fit_results$table

estimate_for_table <-
  `colnames<-`(
    cbind.data.frame(
      unlist(fit_results$coefficients[,1])
      ,names(unlist(fit_results$coefficients[,1]))
    ), c("estimate","rows"))$estimate

stderror_for_table <-
  `colnames<-`(
    cbind.data.frame(
      unlist(fit_results$coefficients[,2])
      ,names(unlist(fit_results$coefficients[,2]))
    ), c("stderror","rows"))$stderror

estimate_for_table
stderror_for_table

results_for_table$estimate <- estimate_for_table
results_for_table$StdError <- stderror_for_table

results_for_table <- results_for_table[c(1,2,7,3,4,5,6)]

results_for_table$estimate <- sprintf("%.3f", results_for_table$estimate)
results_for_table$StdError <- sprintf("%.3f", results_for_table$StdError)

# library(Hmisc)
# 
# var.labels = 
#   c(
#     term        = "Predictor" 
#     , "estimate"  = "$b$" 
#     , "StdError"  = "$S.E.$"
#     , conf.int  = "95\\% CI" 
#     , statistic = "$t$" 
#     , df        = "$\\mathit{df}$" 
#     , p.value   = "$p$" 
#     )
# 
# label(results_for_table) = as.list(var.labels[match(names(results_for_table), names(var.labels))])

results_for_table$term <- c(
  "Intercept"
  ,"Power Distance"
  ,"Individualism"
  ,"Masculinity"
  ,"Uncertainty Avoidance"
  ,"Long Term Orientation"
  ,"Indulgence"
  ,"Tightness: Domain General"
  ,"Tightness: Domain Specific"
  ,"Tightness: Combination Measure"
)

variable_label(results_for_table$estimate) <- "$b$"
variable_label(results_for_table$StdError) <- "$S.E.$"
variable_label(results_for_table$term) <- "Predictor"

fit <- lm(moral_identity_symbolic ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = x
            )

fit_results <- summary(fit)
fit_results$adj.r.squared
anova(fit)
apa_fit_results <- apa_print(fit)

apa_fit_results$full_result$modelfit$r2
fit$qr
apa_fit_results$table
results_for_table <- apa_fit_results$table

estimate_for_table <-
  `colnames<-`(
    cbind.data.frame(
      unlist(fit_results$coefficients[,1])
      ,names(unlist(fit_results$coefficients[,1]))
    ), c("estimate","rows"))$estimate

stderror_for_table <-
  `colnames<-`(
    cbind.data.frame(
      unlist(fit_results$coefficients[,2])
      ,names(unlist(fit_results$coefficients[,2]))
    ), c("stderror","rows"))$stderror

estimate_for_table
stderror_for_table

results_for_table$estimate <- estimate_for_table
results_for_table$StdError <- stderror_for_table

results_for_table <- results_for_table[c(1,2,7,3,4,5,6)]

results_for_table$estimate <- sprintf("%.3f", results_for_table$estimate)
results_for_table$StdError <- sprintf("%.3f", results_for_table$StdError)

# library(Hmisc)
# 
# var.labels = 
#   c(
#     term        = "Predictor" 
#     , "estimate"  = "$b$" 
#     , "StdError"  = "$S.E.$"
#     , conf.int  = "95\\% CI" 
#     , statistic = "$t$" 
#     , df        = "$\\mathit{df}$" 
#     , p.value   = "$p$" 
#     )
# 
# label(results_for_table) = as.list(var.labels[match(names(results_for_table), names(var.labels))])

results_for_table$term <- c(
  "Intercept"
  ,"Power Distance"
  ,"Individualism"
  ,"Masculinity"
  ,"Uncertainty Avoidance"
  ,"Long Term Orientation"
  ,"Indulgence"
  ,"Tightness: Domain General"
  ,"Tightness: Domain Specific"
  ,"Tightness: Combination Measure"
)

variable_label(results_for_table$estimate) <- "$b$"
variable_label(results_for_table$StdError) <- "$S.E.$"
variable_label(results_for_table$term) <- "Predictor"

@@

Overall the model was a significant predictor of symbolization `r apa_fit_results$full_result$modelfit$r2`. The full regression results are displayed in Table\ \@ref(tab:regressionTable).

```{r regressionTable, include=TRUE}
apa_table(
  results_for_table
#  , align = c("c", "c", "c")
  , caption = "Full Regression Results for each country level variable predicting symbolization"
  )

In line with H3a greater power distance was associated with higher symbolization scores.

We proposed two competing hypotheses for the relationship between symbolization and symbolization. H3b~1~ predicted that symbolization would be negatively related to individualism (i.e., higher symbolization would be observed in more collectivist cultures). H3b~2~ predicted that individualism and symbolization would be positively associated. Our results support H3b~2~ (over H3b~1~), suggesting that members of more individualistic societies show greater symbolization scores.

We predicted that members of more masculine cultures would score higher in symbolization (H3c). Our results were in line with this prediction.

For H3d we predicted that uncertainty avoidance would be related to higher symbolization. This was not supported, and we found no relationship between symbolization and uncertainty avoidance.

We predicted a negative association between long-term orientation and symbolization (H3e), that is, we expected participants in societies showing greater long-term orientation to present with lower symbolization scores. Our results supported this hypothesis.

Regarding indulgence/restraint, we predicted (H3f) that greater indulgence would be related to higher symbolization scores, and this hypothesis was supported.

We employed measures of three dimensions of cultural tightness, domain-general, domain-specific, and combination, and predicted that symbolization would be positively associated with each dimension. Our hypothesis was supported for only one dimension (domain-general). Interestingly, both domain-specific and combination dimensions of cultural tightness were negatively related to symbolization.

### 2023-02-10 supp_H1.Rmd
created links to supplementary within the main results
heat maps and flag plots added

```{r}
rm(list = ls())
library(tidyverse)
library(plyr)
library(psych)
library(skimr)
library(corrplot)
library(Hmisc)
#library(psy)
library(afex)
#devtools::install_github("cillianmiltown/R_desnum")
library(desnum)
library(papaja)
library(purrr)
#install.packages("interactions")
library(interactions)
library(kableExtra)
#devtools::install_github("crsh/papaja")
library("papaja")
library(lme4)
library(car)
library(ggplot2)
library(nlme)
#install.packages("reshape")
library(reshape)
library(corx)
library(lsr)
#install.packages("Cairo")
#library(Cairo)
library(foreign)
library(ltm)
library("ggpubr")
#install.packages("rworldmap")
library(rworldmap)
#devtools::install_github("rensa/ggflags")
library(ggflags)
#devtools::install_github("schliebs/ggoxford")
library(ggoxford)
library(ggforce)
library(ggbeeswarm)
library(countrycode)
```

@@

test <- `colnames<-`(test, c("Total N","n Female","N male"))

@@

@@

>>>>

```{r}
rm(list = ls())
library(tidyverse)
library(plyr)
library(psych)
library(skimr)
library(corrplot)
library(Hmisc)
#library(psy)
library(afex)
#devtools::install_github("cillianmiltown/R_desnum")
library(desnum)
library(papaja)
library(purrr)
#install.packages("interactions")
library(interactions)
library(kableExtra)
#devtools::install_github("crsh/papaja")
library("papaja")
library(lme4)
library(car)
library(ggplot2)
library(nlme)
#install.packages("reshape")
library(reshape)
library(corx)
library(lsr)
#install.packages("Cairo")
#library(Cairo)
library(foreign)
library(ltm)
library("ggpubr")
#install.packages("rworldmap")
library(rworldmap)
#devtools::install_github("rensa/ggflags")
library(ggflags)
#devtools::install_github("schliebs/ggoxford")
library(ggoxford)
library(ggforce)
library(ggbeeswarm)
library(countrycode)
library(sf)
# install.packages("rnaturalearth")
# install.packages("rnaturalearthdata")
library("rnaturalearth")
library("rnaturalearthdata")

@@

test <- `colnames<-`(test, c("Total N","n Female","n Male"))

@@

### Heat Map

```{r, include=FALSE}

world <- ne_countries(scale = "medium", returnclass = "sf")
world

#country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")

test$country <- rownames(test)
test$name <- test$country

test_sig <- test[which(test$p<.05),]
test_sig$mean_diff <- test_sig$`mean F`-test_sig$`mean M`

test_non_sig <- test[which(test$p>.05),]
test_non_sig$mean_diff <- rep(0, length(test_non_sig$`mean F`))
rbind.data.frame(test_sig,test_non_sig)
test <- rbind.data.frame(test_sig,test_non_sig)

#test <- test[which(test$p<.05),]

test1 <- left_join(world,test, by = "name")

#test1$mean_diff <- test1$`mean F`-test1$`mean M`

#install.packages("sf")
#library(sf)
g1 <- ggplot(test1
       ,aes(fill=mean_diff)
       )+
  geom_sf()+
  scale_fill_gradient2(
  low = "blue", #muted("red"),
  mid = "grey90",
  high = "red", #muted("blue"),
  midpoint = 0,
  space = "Lab",
  na.value = "white",
  guide = "colourbar",
  aesthetics = "fill"
)+
  labs(fill = "Mean\nDifference")+
  theme_bw()+
  theme(#legend.position = "none"
   plot.title=element_text(#family="Times",
    size=12
  )
  , legend.text=element_text(#family="Times",
    size=8
  )
  , legend.title=element_text(#family="Times",
    size=10
  )
  , axis.text=element_text(#family="Times",
    colour = "black",
    size=8
  )
  , axis.ticks.x = element_blank()
  , axis.title=element_text(#family="Times",
    size=12
  )
  , strip.text=element_text(#family = "Times",
    size = 12
  )
  , strip.background = element_rect(fill = NA, size = 1,
                                    colour = "white"
  )
  , panel.border = element_blank()
  , axis.line.x = element_line(size = 0.1
                               , linetype = "solid", colour = "black")
  , axis.line.y = # element_blank()
    element_line(size = 0.1
                 , linetype = "solid", colour = "black")
  #, legend.position="none"
  , panel.spacing = unit(2, "lines")
  )

ggsave("plots/internalization_heatmap.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```{r, InternalizationHeatMAp,fig.cap="Effect size for gender differences in Internalization across countries",include=TRUE}
suppressWarnings(print(g1))

@@

### Heat Map

```{r, include=FALSE}

world <- ne_countries(scale = "medium", returnclass = "sf")
world

#country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")

test$country <- rownames(test)
test$name <- test$country

test_sig <- test[which(test$p<.05),]
test_sig$mean_diff <- test_sig$`mean F`-test_sig$`mean M`

test_non_sig <- test[which(test$p>.05),]
test_non_sig$mean_diff <- rep(0, length(test_non_sig$`mean F`))
test_non_sig$`mean F`
length(test_non_sig$`mean F`)
test <- rbind.data.frame(test_sig,test_non_sig)

test1 <- left_join(world,test, by = "name")

#test1$mean_diff <- test1$`mean F`-test1$`mean M`

#install.packages("sf")
#library(sf)
g1 <- ggplot(test1
       ,aes(fill=mean_diff)
       )+
  geom_sf()+
  scale_fill_gradient2(
  low = "blue", #muted("red"),
  mid = "grey95",
  high = "red", #muted("blue"),
  midpoint = 0,
  space = "Lab",
  na.value = "white",
  guide = "colourbar",
  aesthetics = "fill"
)+
  labs(fill = "Mean\nDifference")+
  theme_bw()+
  theme(#legend.position = "none"
   plot.title=element_text(#family="Times",
    size=12
  )
  , legend.text=element_text(#family="Times",
    size=8
  )
  , legend.title=element_text(#family="Times",
    size=10
  )
  , axis.text=element_text(#family="Times",
    colour = "black",
    size=8
  )
  , axis.ticks.x = element_blank()
  , axis.title=element_text(#family="Times",
    size=12
  )
  , strip.text=element_text(#family = "Times",
    size = 12
  )
  , strip.background = element_rect(fill = NA, size = 1,
                                    colour = "white"
  )
  , panel.border = element_blank()
  , axis.line.x = element_line(size = 0.1
                               , linetype = "solid", colour = "black")
  , axis.line.y = # element_blank()
    element_line(size = 0.1
                 , linetype = "solid", colour = "black")
  #, legend.position="none"
  , panel.spacing = unit(2, "lines")
  )

ggsave("plots/symbolization_heatmap.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```{r, SymbolizationHeatMAp,fig.cap="Effect size for gender differences in Symbolization across countries",include=TRUE}
suppressWarnings(print(g1))
